---
title: "Week4_part1_CIs and t-tests"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## 1. confidence intervals

```{r}
otter_length <- c(38, 41, 50, 27, 32, 41, 48, 60, 43)

t.test(otter_length)

```

## T-tests (1-sample t-test)

See a claim: mean otter length is 50 inches

```{r}
otter_test <- t.test(x = otter_length, mu = 50)
otter_test
```

try not to think about whether p-value is significant. take away - is it possible that my sample was taking from a population with a mean of 50, but there's only a 4.44% chance if the population mean is 50 inches that I could have taken a random sample from that pop and found a sample mean that is at least as different as mine is from that null hypothesis value.

## Two-sample t-test

```{r}
desert_bighorns <- c(32, 44, 18, 26, 50, 33, 42, 20)
sierra_bighorns <- c(28, 31, 40, 42, 26, 29, 31)

t.test(x = desert_bighorns, y = sierra_bighorns)
```

.8849 means that theres 88.49% probability that these samples with means at least as different as ours are.






